---
title: "Data Analysis for Give me Gestalt - Cubist Art Experiment"
output:
  html_document:
    df_print: paged
Authors: Group 03
---

# Instructions

## Required R packages
* `tidyverse` (or `ggplot2`, `dplyr`, `purrr`, `tibble`)
* `brms`
* `devtools` (for installing `faintr`)
* `rstan`
* `faintr` (install with `devtools`)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

Load the required packages and set a seed for the random number generator.
```{r}
library(tidyverse)

library(rstan)
# set cores to use to the total number of cores (minimally 4)
options(mc.cores = max(parallel::detectCores(), 4))
# save a compiled version of the Stan model file
rstan_options(auto_write = TRUE)

library(brms)

library(gmodels)

# install faintr with devtools::install_github('michael-franke/bayes_mixed_regression_tutorial/faintr', build_vignettes = TRUE))
library(faintr)

set.seed(123)

```

Step 1. Read the data and take a glimpse of it.
---

```{r}
data_raw <- read_csv("results_71_givemegestalt_group3_group3.csv")
glimpse(data_raw)
```


Step 2. Select only the columns of interest and filter trials that are not interesting for the calculations.
Change data type of the responses to double and submission_id to factor. 
Delete invalid participants.
---

```{r}
data_selection <- select(data_raw, submission_id, snellen_result, is_expert, age, gender, trial_name, trial_number, fileID, response, RT, timeSpent, comments)
data_filtered <- filter(data_selection, trial_name != "test_snellen", trial_name != "b0_expert")
data_mut <- mutate(data_filtered, response = as.double(response), submission_id = factor(submission_id))

show(data_selection)
show(data_filtered)
show(data_mut)

# 3 participants only rated "1" in both blocks, one participant only rated "7", one gave a invalid input for the Snellen test, we exclude them:
data_clean <- filter(data_mut, submission_id != 607, submission_id != 736, submission_id != 475, submission_id != 480, submission_id != 726)
show(data_clean)
```
Step.3 Demografics
---
```{r}
data_rawdemografics <- select(data_clean, submission_id, age, gender, is_expert, snellen_result, comments)
data_demografics <- dplyr::distinct(group_by(data_rawdemografics, submission_id))
show(data_demografics[order(data_demografics$submission_id),])
```

Total number of participents:
```{r}
length(unique(data_clean$submission_id))
```
Detecting the gender data provided and their count:
```{r}
data_gender_male <- filter(data_clean,gender == "male")
data_gender_female <- filter(data_clean,gender == "female")
data_gender_diverse <- filter(data_clean,gender == "divers")
length(data_gender_male$gender)/120
length(data_gender_female$gender)/120
length(data_gender_diverse$gender)/120
sum(is.na(data_clean$gender))/120 # counting how many NA are there.
```
There are total 33 male participents, 57 female and 2 of them identify their gender as diverse and 2 of them did not submitted the data about gender.

Data set according to age:
```{r}
data_age_below_20 <- filter(data_clean,age <= 19)
data_age_20_40<-filter(data_clean,age>=20&age<=40)
data_age_ab_40 <- filter(data_clean,age > 40)
#divide by 120 beacuse there are 120 entries per person
length(data_age_below_20$age)/120 
length(data_age_20_40$age)/120
length(data_age_ab_40$age)/120
sum(is.na(data_clean$age))/120
```
From all participants there are in total 14 participants, who are below age of 20, 69 are in range of 20 - 40 and 10 are in range of 41 to 63. 1 participants did not give data for age.

Step 4. Split data according to trial (b1: Liking, b2: Detactability).
---

```{r}
#Data with all participants
data_b1 <- filter(data_clean, trial_name == "b1_exp")
data_b2 <- filter(data_clean, trial_name == "b2_exp")
```

Step 5. Age and Liking/ Age and Detectability
---
```{r}
data_b1_age <- group_by(data_b1, age) %>% summarise(mean_Like = mean(response))
data_b2_age <- group_by(data_b2, age) %>% summarise(mean_Detect = mean(response))

final_data_age0 <- merge(x = data_b2_age, y = data_b1_age, by = "age")
final_data_age <- na.omit(final_data_age0) # delete NA.
show(final_data_age)

ggplot(final_data_age, aes(x = age, y = mean_Like)) + geom_point() + geom_smooth(method = "lm")
ggplot(final_data_age, aes(x = age, y = mean_Detect)) + geom_point() + geom_smooth(method = "lm")

cor(final_data_age$age, final_data_age$mean_Like)
cor(final_data_age$age, final_data_age$mean_Detect)

summary(lm(final_data_age$mean_Like ~ final_data_age$age))
```
Result: No correlation.